Seasonality of submesoscale dynamics in the Kuroshio Extension

### 2016-09-26 writeup/rocha_etal_draft-like.tex
Adds missing refs to main text

Fundamentally, the upper-ocean density structure is well-captured by both LLC simulations:
a comparison with Argo climatology shows that both simulations skillfully represent the Kuroshio
Extension stratification and its seasonal variability  (supporting information). Moreover, model smoothed
fields have eddy kinetic energy (EKE) levels ($0.041$ m$^2$ s$^{-2}$) similar to Jason II across-track
geostrophic EKE ($0.036$ m$^2$ s$^{-2}$) and gridded geostrophic EKE ($0.032$ m$^2$ s$^{-2}$).

@@

\cite{dasaro1978} showed that the velocity of linear internal waves
in the mixed layer strongly depends on the density jump at the mixed layer
base, with largest velocities when the jump is strongest.
In summer, the shallow mixed layer overlays a strong seasonal pycnocline,
and thus the internal waves projection onto the mixed layer may be stronger
according to \cite{dasaro1978}'s arguments. An
alternative explanation is that the shape of the baroclinic modes
changes seasonally (supporting information).

@@

>>>>

Fundamentally, the upper-ocean density structure is well-captured by both LLC simulations:
a comparison with Argo climatology \citep[updated from ][]{roemmich_gilson2009} shows that both simulations skillfully represent the Kuroshio
Extension stratification and its seasonal variability  (supporting information). Moreover, model smoothed
fields have eddy kinetic energy (EKE) levels ($0.041$ m$^2$ s$^{-2}$) similar to Jason II across-track
geostrophic EKE ($0.036$ m$^2$ s$^{-2}$) and gridded geostrophic EKE ($0.032$ m$^2$ s$^{-2}$).

@@

\cite{dasaro1978} showed that the velocity of linear internal waves
in the mixed layer strongly depends on the density jump at the mixed layer
base, with largest velocities when the jump is strongest.
In summer, the shallow mixed layer overlays a strong seasonal pycnocline,
and thus the internal waves projection onto the mixed layer may be stronger
according to \cite{dasaro1978}'s arguments. An
alternative explanation is that the shape of the baroclinic modes
changes seasonally  \citep[see World Ocean Atlas 2013,
][modal shapes in the
supporting information]{levitus_etal2013}.

@@

  \bibitem[{\textit{Roemmich and Gilson}(2009)}]{roemmich_gilson2009}
    Roemmich, D., and J.~Gilson (2009), {The 2004--2008 mean and annual cycle of
      temperature, salinity, and steric height in the global ocean from the Argo
      Program}, \textit{Progress in Oceanography}, \textit{82}(2), 81--100.

### 2016-09-26 writeup/rocha_etal_supporting-info.tex
Adds missing refs to main text

 \begin{figure}
    \begin{center}
      \setfigurenum{S4}
      \includegraphics[width=40pc]{figs/figS4.pdf}
   \caption{Potential density: a comparison between Roemmich-Gilson Argo
           climatology [updates from \cite{roemmich_gilson2009}] (a, b) and the 1/24$^\circ$ (c, d)
           and  1/48$^\circ$ (e, f) LLC simulations. The Argo climatology is smoother
           owing to lower resolution and long-term averaging. Nonetheless, simulations reproduce the strong
           seasonality in the stratification. The upper ocean is weakly stratified in late winter/early fall
           and re-stratifies in summer. Argo climatology and LLC simulations mixed-layer depths are consistent
            during all seasons (not shown). The Argo climatology is available online at
           \texttt{http://sio-argo.ucsd.edu/RG\_Climatology.html}.}
   \label{figS2_1}
   \end{center}
 \end{figure}

>>>>

 \begin{figure}
    \begin{center}
      \setfigurenum{S4}
      \includegraphics[width=40pc]{figs/figS4.pdf}
   \caption{Potential density: a comparison between Roemmich-Gilson Argo
           climatology [updated from \cite{roemmich_gilson2009}] (a, b) and the 1/24$^\circ$ (c, d)
           and  1/48$^\circ$ (e, f) LLC simulations. The Argo climatology is smoother
           owing to lower resolution and long-term averaging. Nonetheless, simulations reproduce the strong
           seasonality in the stratification. The upper ocean is weakly stratified in late winter/early fall
           and re-stratifies in summer. Argo climatology and LLC simulations mixed-layer depths are consistent
            during all seasons (not shown). The Argo climatology is available online at
           \texttt{http://sio-argo.ucsd.edu/RG\_Climatology.html}.}
   \label{figS2_1}
   \end{center}
 \end{figure}
